---
title: 'A3: SPL Library Checkouts'
output:
  html_document: default
  pdf_document: default
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library("dplyr")
library("ggplot2")
```
### Introduction

I have included three charts that shows trends of people's preference over the type of books including, Ebooks, printed books, and sound disc. The reason why I chose these three material types is that I thought the comparison of the three materials are going to show us the changing trend in each material type and the overall trends. 

### Summary Information

The following 6 values show the number of checkouts or the mean of the checkouts for each materials. I am particulary interested in the material types for printed books, ebooks, and sound disc because those three materials are the one that I am familiar with. 

- What is the average number of checkouts for each item?
The average number of checkouts for each item (4 values total):

EBOOK: 3.403392
BOOK: 2.847207
AUDIOBOOK: 4.761147
SOUNDDISC: 1.596941

- What is the month or year with the most checkouts for ebooks?
The month with the most checkouts for ebooks was September.

- What is the month or year with the least checkouts for ebooks?
The month with the least checkouts for ebooks was June.

- How has the number of print book checkouts changed over time?
The average number of checkouts for each month has been changed over time as follows:

2022.1 -2.965044
2022.2 - 2.74244
2022.3 - 2.911105
2022.4 - 2.805779
2022.5 - 2.828401
2022.6 - 2.905877
2022.7 - 2.787964
2022.8 - 2.904679
2022.9 - 2.808679
2022.10 - 2.84046
2022.11 - 2.818921
2022.12 - 2.694061
2023.1 - 2.965565


### The Dataset

- Who collected/published the data?
The Seattle Public Library

- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
Months, Year, Usage Class, Checkout type, Material type, number of checkouts, Book Title, ISBN, Creator, Subjects, Publisher, Publication Year

- How was the data collected or generated?
The data is collecteed by using The Socrata Open Data API and it allows you to programmatically access a wealth of open data resources from governments, non-profits, and NGOs around the world.

- Why was the data collected?  
For the purpose of increasing the quality of life for our residents; increasing transparency, accountability and comparability; promoting economic development and research; and improving internal performance management.

- What, if any, ethical questions do you need to consider when working with this data?
I wonder the location of Seattle Public Libraries and want to know whether it is easy for everyone to access so that the result of data is equally collected.

- What are possible limitations or problems with this data?   (at least 200 words)
One of the possible limitations from this data are who did they collected the data from. Although Seattle Public Libraries are located in various location in Seattle, it is unclear that location of the libraries is easily approachable to everyone. In my personal experience, the public library was located in Wedgwood area where the age range is higher and majority of the visitors are white. If this is the case, we are not analyzing the data and cannot draw conclusions that can be applied to every sector of people in Seattle Area. Furthermore, since the age range of the neighborhood is higher than other neighborhoods, the data cannot be collected from all of the age ranges. This dataset might not represent the holistic view and type of people who got collected from the Seattle Public Library. Lastly, in order to figure the trend of checkouts in Material Type can be limited because there are so many people who purchase books from Amazon and other online based bookstores. This may also lay different results from other data collection which means that the data set from Seattle Public Library does not represent the current trend of book preferences and other possible trends.


### First Trends Over Time Chart

The chart below shows the trend of number of checkouts for Ebooks in 2022. The reason why I included this chart is to see how people's preference of Ebook over printed books as the time goes. The chart shows that the number of checkouts for EBOOK is slowly increasing.   

```{r, echo = FALSE, warning = FALSE, code = readLines("chart1_example.R")}
```

### Second Trends Over Time Chart

The chart below shows the trend of number of checkouts for printed books in 2022. The reason why I included this chart is to see how people's preference of printed books has been remained the same of decreased over time. The chart shows that the number of checkouts for printed books has been decreased over time throughout the year of 2022. 

```{r, echo = FALSE, code = readLines("chart2_example.R")}
```

### Your Choice

The chart below shows the trend of number of checkouts for sound disc in 2022. The reason why I included this chart is to see how people's preference of sound disc has been remained the same of decreased over time. Surprisingly, the chart shows that the number of checkouts for sound disc has been increased dramatically over time throughout the year of 2022. 

```{r, echo = FALSE, code = readLines("Chart3.R")}
```


